### 2023-01-22 appendix_properties_of_B/appendix.tex
finito
first iteration of changes for reviewer 2 and response to reviewer 2 comments (to do: reviewer 1 changes and responses)
post-reviews, pre supervisor feedback

Recall that the coefficients \({\boldsymbol a}_{k,i}(t)\) can be used to construct an approximate solution to a differential equation at time \(t\) as \(u_{k,i}(x,t)={\boldsymbol a}_{k,i}(t)\boldsymbol \phi_k(x)\tr{}.\) For \(i\in\calS,\,k\in\mathcal K,\,r\in\{1,...,p_k\}\), define \(\alpha_{k,i}^r(t) := a_{k,i}^r(t)\displaystyle\int_{x=y_k}^{y_{k+1}}\phi^r_k(x)\wrt x,\) and row-vectors \(\boldsymbol \alpha_{k,i}(t)=(\alpha_{k,i}^r(t))_{r\in\{1,...,p_k\}}\). Motivated by the fact that we may be interested in approximations of the probabilities \(\mathbb P(X(t)\in\calD_{k,i},\varphi(t)=i)\) rather than the function \(u_{k,i}\) itself, we can pose the problem equivalently in terms of the integrals 
\[\mathbb P\left(X(t)\in\calD_{k,i},\varphi(t)=i\right)\approx{\boldsymbol a}_{k,i}(t)\int_{x\in\calD_{k,i}}\boldsymbol \phi_k(x)\tr{}\wrt x={\boldsymbol \alpha}_{k,i}(t)\boldsymbol 1.\] 
Define
\[\boldsymbol \alpha_k(t) = (\boldsymbol \alpha_{k,i}(t))_{i\in\calS},\mbox{ and } \boldsymbol \alpha(t)=(\boldsymbol \alpha_k(t)))_{k\in\mathcal K},\]
and matrices 
\begin{align*}
\bs P_k &= \diag\left(\int_{x=y_k}^{y_{k+1}}\phi^r_k(x)\wrt x\right)_{ r\in\{1,...,p_k\}},\, k\in\mathcal K^\circ,
\\\bs P &=\left[\begin{array}{ccc}
		\bs I_{N}\otimes \bs P_0 & &\\
		& \ddots &\\
		& & \bs I_{N}\otimes \bs P_K
	\end{array}\right].
\end{align*}
By choosing the basis \(\{\phi_{k}^r\}_{r\in\{1,...,p_k\},k\in\mathcal K^\circ}\) such that \(\int_{x=y_k}^{y_{k+1}}\phi^r_k(x)\wrt x\neq 0\) for all \(r,k\), then \(\bs P\) is invertible. This is the case for the Lagrange polynomials, but not, for example, for the Legendre polynomials. We can (loosely) interpret the new coefficients \(\alpha_{k,i}^r(t)\) as representing the amount of probability captured by the basis function \(\phi^r_k(x)\) in phase \(i\).

@@

 {  {\mathfrak{\bs B}}}^{{-1}0} &:= \bs T_{{-1}+}\otimes\left( \boldsymbol\phi_0(0)\bs M_0^{-1}\bs P_0\right),

@@

 \\ {  {\mathfrak{\bs B}}}^{0{-1}} &:=-\left[c_ip_{ij}^{-1} 1{(c_i<0)}\right]_{i\in\calS,j\in\calS_{{-1}}}\otimes \bs P_0^{-1}\boldsymbol \phi_0(0)\tr{},

@@

 \\ {  {\mathfrak{\bs B}}}^{{K+1} K} &:= \bs T_{{K+1}-}\otimes \left(\boldsymbol\phi_K(b)\bs M_K^{-1}\bs P_K\right)

@@

 \\ {  {\mathfrak{\bs B}}}^{K {K+1}} &:= \left[c_ip_{ij}^{K+1} 1{(c_i>0)}\right]_{i\in\calS,j\in\calS_{K+1}} \otimes  \bs P_K^{-1} \boldsymbol\phi_K(b)\tr{},

@@

 \\\mathfrak{\bs B}^{kk}_{ij} &:= \begin{cases}

@@

 \\\mathfrak{\bs B}^{00}_{ij} &:= \begin{cases}

@@

T_{ij}\bs I_{p_0} - c_ip_{ij}^{-1} 1(c_i<0)\bs F_i^{00}\bs M_0^{-1}\bs P_0 & i \neq j,

@@

\\\mathfrak{\bs B}^{KK}_{ij} &:= \begin{cases}

@@

T_{ij}\bs I_{p_K} + c_ip_{ij}^{K+1} 1(c_i>0)\bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K & i \neq j,

@@

 \\\mathfrak{\bs B}^{k,k+1}_{ij} &:= \begin{cases}

@@

 \\\mathfrak{\bs B}^{k-1,k}_{ij} &:= \begin{cases}

@@

	Now, with the above observations made, we first claim that, for \(c_i>0\), and \(k=0,1,...,K-1\), 
	\begin{align*}
		\sum_{j\in\calS}\mathfrak{\bs B}^{kk}_{ij}\bs 1 + \mathfrak{\bs B}^{kk+1}_{ij}\bs 1
		&=\sum_{j\in\calS}T_{ij}\bs I_{p_k}\bs 1 + c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_k^{-1}\bs P_k\boldsymbol 1 
		\\&=\bs 0.
	\end{align*}
	The first sum is zero since \(\bs T\) is a generator of a continuous-time Markov chain. This leaves the other two terms, which, using our observations, we get 
	\begin{align*}
		& c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_{k+1}^{-1}\bs P_{k+1}\boldsymbol 1
		\\&= c_i \bs P_k^{-1}\bs F_i^{kk} \bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs G_k\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_{k+1}^{-1}\bs P_{k+1}\boldsymbol 1 
		\\&= \boldsymbol 0.
	\end{align*}
	For \(c_i>0\) and \(k=K\), 
	\begin{align*}
		&\sum_{j\in\calS}\mathfrak{\bs B}^{KK}_{ij}\bs 1 + \mathfrak{\bs B}^{K{K+1}}_{ij}\bs 1
		\\&= \sum_{j\in\calS}T_{ij}\bs I_{p_K}\bs 1-\sum_{j\in\calS_-} c_ip_{ij}^{K+1} \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K \bs 1 -\sum_{j\in\calS_{{K+1} }}c_ip_{ij}^{K+1} \bs P_K^{-1}\boldsymbol \phi_K(0)\tr{}\bs 1 
		\\&\quad{} + c_i \bs P_K^{-1}(\bs F_i^{KK}+\bs G_K)\bs M_K^{-1}\bs P_K\boldsymbol 1 
		\\&= -\sum_{j\in\calS_-} c_ip_{ij}^{K+1} \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K \bs 1 
		\\&{}\quad-\sum_{j\in\calS_{{K+1}}}c_ip_{ij}^{K+1} \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K\bs 1+ c_i \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K\boldsymbol 1
		\\&\quad{}+ c_i \bs P_K^{-1}\bs G_K\bs M_K^{-1}\bs P_K\boldsymbol 1
		%
		\\&= - c_i \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K \bs 1 + c_i \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K\boldsymbol 1 + c_i \bs P_K^{-1}\bs G_K\boldsymbol 1
		\\&= \bs 0.
	\end{align*}
	% Similarly, for \(c_i<0\), and row-vectors \(\boldsymbol b\) and \(\boldsymbol d\) of length \(p_k\) and \(p_{k-1}\), respectively, 
	% \begin{align*}
	% 	\bs F_i^{kk}\boldsymbol b &= \boldsymbol \phi^k(y_{k})\tr{} \boldsymbol \phi^k(y_{k})\boldsymbol b \\&= (\bs e^{k}_{1})\tr{} \bs e_{1}^{k}\bs b  \\&= b_{1}(\boldsymbol e_{1}^k)\tr{} 
	% 	%
	% 	\\\bs F_i^{k,k-1}\boldsymbol d &= -\boldsymbol \phi^{k}(y_{k})\tr{} \boldsymbol \phi^{k-1}(y_{k})\boldsymbol d \\&= -(\bs e^{k}_{1})\tr{} \bs e_{p_{k-1}}^{k-1}\bs d \\&= -d_{p_{k-1}}(\boldsymbol e_{1}^k)\tr{}.
	% 	\end{align*}

		Similarly, for \(c_i<0\) and \(k=1,...,K\), using the same arguments as before we have
	\begin{align*}
		\sum_{j\in\calS}\mathfrak{\bs B}^{kk}_{ij}\bs 1 + \mathfrak{\bs B}^{kk-1}_{ij}\bs 1
		&=\sum_{j\in\calS}T_{ij}\bs I_{p_k}\bs 1 + c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k-1}\bs M_k^{-1}\bs P_k\boldsymbol 1
		% \\&= \boldsymbol 0 + c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_{k-1}^{-1}\bs P_{k-1}\boldsymbol 1
		% \\&= c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k-1}\boldsymbol 1
		% \\&= c_i \bs P_k^{-1}\bs F_i^{kk}\boldsymbol 1 + c_i \bs P_k^{-1}\bs G_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k-1}\boldsymbol 1
		% \\&= c_i \bs P_k^{-1}(\boldsymbol e_{1}^k)\tr{} + \boldsymbol 0 + c_i \bs P_k^{-1}(-\boldsymbol e_{1}^k)\tr{}
		\\&= \boldsymbol 0.
	\end{align*}
	For \(c_i<0\) and \(k=K\), 
	\begin{align*}
		\sum_{j\in\calS}\mathfrak{\bs B}^{00}_{ij}\bs 1 + \mathfrak{\bs B}^{0{-1}}_{ij}\bs 1
		&= \sum_{j\in\calS}T_{ij}\bs I_{p_0}\bs 1-\sum_{j\in\calS_+} c_ip_{ij}^{-1} \bs P_0^{-1}\bs F_i^{00}\bs M_0^{-1}\bs P_0 \bs 1 -\sum_{j\in\calS_{{-1} }}c_ip_{ij}^{-1} \bs P_0^{-1}\boldsymbol \phi_0(0)\tr{}\bs 1 
		\\&\quad{} + c_i \bs P_0^{-1}(\bs F_i^{0,0}+\bs G_0)\bs M_0^{-1}\bs P_0\boldsymbol 1 
		% \\&= -\sum_{j\in\calS_+} c_ip_{ij}^{-1} \bs P_1^{-1}\bs F_i^{11}\bs M_1^{-1}\bs P_1 \bs 1 -\sum_{j\in\calS_{{-1} }}c_ip_{ij}^{-1} \bs P_1^{-1}\bs F_i^{11}\bs M_1^{-1}\bs P_1\bs 1+ c_i \bs P_1^{-1}\bs F_i^{1,1}\bs M_1^{-1}\bs P_1\boldsymbol 1
		% \\&\quad{}+ c_i \bs P_1^{-1}\bs G_1\bs M_1^{-1}\bs P_1\boldsymbol 1
		% %
		% \\&= - c_i \bs P_1^{-1}\bs F_i^{11}\bs M_1^{-1}\bs P_1 \bs 1 + c_i \bs P_1^{-1}\bs F_i^{1,1}\bs M_1^{-1}\bs P_1\boldsymbol 1 + c_i \bs P_1^{-1}\bs G_1\boldsymbol 1
		\\&= \bs 0.
	\end{align*}

>>>>

Recall that the coefficients \({\boldsymbol a}_{k,i}(t)\) can be used to construct an approximate solution to a differential equation at time \(t\) as \(u_{k,i}(x,t)={\boldsymbol a}_{k,i}(t)\boldsymbol \phi_k(x)\tr{}.\) For \(i\in\calS,\,k\in\mathcal K,\,r\in\{1,...,p_k\}\), define \(\alpha_{k,i}^r(t) = a_{k,i}^r(t)\displaystyle\int_{x=y_k}^{y_{k+1}}\phi^r_k(x)\wrt x,\) and row-vectors \(\boldsymbol \alpha_{k,i}(t)=(\alpha_{k,i}^r(t))_{r\in\{1,...,p_k\}}\). Motivated by the fact that we may be interested in approximations of the probabilities \(\mathbb P(X(t)\in\calD_{k,i},\varphi(t)=i)\) rather than the function \(u_{k,i}\) itself, we can pose the problem equivalently in terms of the integrals 
\[\mathbb P\left(X(t)\in\calD_{k,i},\varphi(t)=i\right)\approx{\boldsymbol a}_{k,i}(t)\int_{x\in\calD_{k,i}}\boldsymbol \phi_k(x)\tr{}\wrt x={\boldsymbol \alpha}_{k,i}(t)\boldsymbol 1.\] 
Define
\[\boldsymbol \alpha_k(t) = (\boldsymbol \alpha_{k,i}(t))_{i\in\calS},\mbox{ and } \boldsymbol \alpha(t)=(\boldsymbol \alpha_k(t)))_{k\in\mathcal K},\]
and matrices 
\begin{align*}
\bs P_k &= \mathrm{diag}\left(\int_{x=y_k}^{y_{k+1}}\phi^r_k(x)\wrt x\right)_{ r\in\{1,...,p_k\}},\, k\in\mathcal K^\circ,
\\\bs P &=\left[\begin{array}{ccc}
		\bs I_{N}\otimes \bs P_0 & &\\
		& \ddots &\\
		& & \bs I_{N}\otimes \bs P_K
	\end{array}\right].
\end{align*}
By choosing the basis \(\{\phi_{k}^r\}_{r\in\{1,...,p_k\},k\in\mathcal K^\circ}\) such that \(\int_{x=y_k}^{y_{k+1}}\phi^r_k(x)\wrt x\neq 0\) for all \(r,k\), then \(\bs P\) is invertible. This is the case for the Lagrange polynomials, but not, for example, for the Legendre polynomials. We can (loosely) interpret the new coefficients \(\alpha_{k,i}^r(t)\) as representing the amount of probability captured by the basis function \(\phi^r_k(x)\) in phase \(i\).

@@

 {  {\mathfrak{\bs B}}}^{{-1}0} &= \bs T_{{-1}+}\otimes\left( \boldsymbol\phi_0(0)\bs M_0^{-1}\bs P_0\right),

@@

 \\ {  {\mathfrak{\bs B}}}^{0{-1}} &=-\left[c_i\widecheck p_{ij} 1{(c_i<0)}\right]_{i\in\calS,j\in\calS_{{-1}}}\otimes \bs P_0^{-1}\boldsymbol \phi_0(0)\tr{},

@@

 \\ {  {\mathfrak{\bs B}}}^{{K+1} K} &= \bs T_{{K+1}-}\otimes \left(\boldsymbol\phi_K(b)\bs M_K^{-1}\bs P_K\right)

@@

 \\ {  {\mathfrak{\bs B}}}^{K {K+1}} &= \left[c_i\widehat p_{ij}  1{(c_i>0)}\right]_{i\in\calS,j\in\calS_{K+1}} \otimes  \bs P_K^{-1} \boldsymbol\phi_K(b)\tr{},

@@

 \\\mathfrak{\bs B}^{kk}_{ij} &= \begin{cases}

@@

 \\\mathfrak{\bs B}^{00}_{ij} &= \begin{cases}

@@

T_{ij}\bs I_{p_0} - c_i\widecheck p_{ij} 1(c_i<0)\bs F_i^{00}\bs M_0^{-1}\bs P_0 & i \neq j,

@@

\\\mathfrak{\bs B}^{KK}_{ij} &= \begin{cases}

@@

T_{ij}\bs I_{p_K} + c_i\widehat p_{ij} 1(c_i>0)\bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K & i \neq j,

@@

 \\\mathfrak{\bs B}^{k,k+1}_{ij} &= \begin{cases}

@@

 \\\mathfrak{\bs B}^{k-1,k}_{ij} &= \begin{cases}

@@

	Now, with the above observations made, we first claim that, for \(c_i>0\), and \(k=0,1,...,K-1\), 
	\begin{align*}
		\sum_{j\in\calS}\mathfrak{\bs B}^{kk}_{ij}\bs 1 + \mathfrak{\bs B}^{kk+1}_{ij}\bs 1
		&=\sum_{j\in\calS}T_{ij}\bs I_{p_k}\bs 1 + c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_k^{-1}\bs P_k\boldsymbol 1 
		\\&=\bs 0.
	\end{align*}
	The first sum is zero since \(\bs T\) is a generator of a continuous-time Markov chain. This leaves the other two terms, which, using our observations, we get 
	\begin{align*}
		& c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_{k+1}^{-1}\bs P_{k+1}\boldsymbol 1
		\\&= c_i \bs P_k^{-1}\bs F_i^{kk} \bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs G_k\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_{k+1}^{-1}\bs P_{k+1}\boldsymbol 1 
		\\&= \boldsymbol 0.
	\end{align*}
	For \(c_i>0\) and \(k=K\), 
	\begin{align*}
		&\sum_{j\in\calS}\mathfrak{\bs B}^{KK}_{ij}\bs 1 + \mathfrak{\bs B}^{K{K+1}}_{ij}\bs 1
		\\&= \sum_{j\in\calS}T_{ij}\bs I_{p_K}\bs 1-\sum_{j\in\calS_-} c_i\widehat p_{ij}  \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K \bs 1 -\sum_{j\in\calS_{{K+1} }}c_i\widehat p_{ij} \bs P_K^{-1}\boldsymbol \phi_K(0)\tr{}\bs 1 
		\\&\quad{} + c_i \bs P_K^{-1}(\bs F_i^{KK}+\bs G_K)\bs M_K^{-1}\bs P_K\boldsymbol 1 
		\\&= -\sum_{j\in\calS_-} c_i\widehat p_{ij} \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K \bs 1 
		\\&{}\quad-\sum_{j\in\calS_{{K+1}}}c_i\widehat p_{ij} \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K\bs 1+ c_i \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K\boldsymbol 1
		\\&\quad{}+ c_i \bs P_K^{-1}\bs G_K\bs M_K^{-1}\bs P_K\boldsymbol 1
		%
		\\&= - c_i \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K \bs 1 + c_i \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K\boldsymbol 1 + c_i \bs P_K^{-1}\bs G_K\boldsymbol 1
		\\&= \bs 0.
	\end{align*}
	% Similarly, for \(c_i<0\), and row-vectors \(\boldsymbol b\) and \(\boldsymbol d\) of length \(p_k\) and \(p_{k-1}\), respectively, 
	% \begin{align*}
	% 	\bs F_i^{kk}\boldsymbol b &= \boldsymbol \phi^k(y_{k})\tr{} \boldsymbol \phi^k(y_{k})\boldsymbol b \\&= (\bs e^{k}_{1})\tr{} \bs e_{1}^{k}\bs b  \\&= b_{1}(\boldsymbol e_{1}^k)\tr{} 
	% 	%
	% 	\\\bs F_i^{k,k-1}\boldsymbol d &= -\boldsymbol \phi^{k}(y_{k})\tr{} \boldsymbol \phi^{k-1}(y_{k})\boldsymbol d \\&= -(\bs e^{k}_{1})\tr{} \bs e_{p_{k-1}}^{k-1}\bs d \\&= -d_{p_{k-1}}(\boldsymbol e_{1}^k)\tr{}.
	% 	\end{align*}

		Similarly, for \(c_i<0\) and \(k=1,...,K\), using the same arguments as before we have
	\begin{align*}
		\sum_{j\in\calS}\mathfrak{\bs B}^{kk}_{ij}\bs 1 + \mathfrak{\bs B}^{kk-1}_{ij}\bs 1
		&=\sum_{j\in\calS}T_{ij}\bs I_{p_k}\bs 1 + c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k-1}\bs M_k^{-1}\bs P_k\boldsymbol 1
		% \\&= \boldsymbol 0 + c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_{k-1}^{-1}\bs P_{k-1}\boldsymbol 1
		% \\&= c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k-1}\boldsymbol 1
		% \\&= c_i \bs P_k^{-1}\bs F_i^{kk}\boldsymbol 1 + c_i \bs P_k^{-1}\bs G_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k-1}\boldsymbol 1
		% \\&= c_i \bs P_k^{-1}(\boldsymbol e_{1}^k)\tr{} + \boldsymbol 0 + c_i \bs P_k^{-1}(-\boldsymbol e_{1}^k)\tr{}
		\\&= \boldsymbol 0.
	\end{align*}
	For \(c_i<0\) and \(k=K\), 
	\begin{align*}
		\sum_{j\in\calS}\mathfrak{\bs B}^{00}_{ij}\bs 1 + \mathfrak{\bs B}^{0{-1}}_{ij}\bs 1
		&= \sum_{j\in\calS}T_{ij}\bs I_{p_0}\bs 1-\sum_{j\in\calS_+} c_i\widecheck p_{ij} \bs P_0^{-1}\bs F_i^{00}\bs M_0^{-1}\bs P_0 \bs 1 -\sum_{j\in\calS_{{-1} }}c_i\widecheck p_{ij} \bs P_0^{-1}\boldsymbol \phi_0(0)\tr{}\bs 1 
		\\&\quad{} + c_i \bs P_0^{-1}(\bs F_i^{0,0}+\bs G_0)\bs M_0^{-1}\bs P_0\boldsymbol 1 
		% \\&= -\sum_{j\in\calS_+} c_ip_{ij}^{-1} \bs P_1^{-1}\bs F_i^{11}\bs M_1^{-1}\bs P_1 \bs 1 -\sum_{j\in\calS_{{-1} }}c_ip_{ij}^{-1} \bs P_1^{-1}\bs F_i^{11}\bs M_1^{-1}\bs P_1\bs 1+ c_i \bs P_1^{-1}\bs F_i^{1,1}\bs M_1^{-1}\bs P_1\boldsymbol 1
		% \\&\quad{}+ c_i \bs P_1^{-1}\bs G_1\bs M_1^{-1}\bs P_1\boldsymbol 1
		% %
		% \\&= - c_i \bs P_1^{-1}\bs F_i^{11}\bs M_1^{-1}\bs P_1 \bs 1 + c_i \bs P_1^{-1}\bs F_i^{1,1}\bs M_1^{-1}\bs P_1\boldsymbol 1 + c_i \bs P_1^{-1}\bs G_1\boldsymbol 1
		\\&= \bs 0.
	\end{align*}
